Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-11 manuscript/manuscript.tex
Minor changes on introduction

\citet{Uieda2016} developed a forward gravity model based on tesseroids with homogeneous densities using the GLQ approximation method.
The GLQ method becomes less accurate when the computation point is closer to the tesseroid \citep{Ku1977} or for smaller GLQ degree. 
Although the model developed by \citet{Uieda2016} uses a second GLQ degree, it ensures the accuracy implementing a modified version of the adaptative discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain distance-size ratio ($D$) is greater than a predefined value that controls the precision of the computation.  \citet{Uieda2016} have also objectively obtained standard values of $D$ for gravity potential, gradients and tensor components comparing the fields generated by a spherical shell, which constitutes a special case of the volume integrals that has analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013}\todo{citar mas??}.
The modifications made by \citet{Uieda2016} to the original adaptative discretization method \citep{Li2011} consist in:
(1) a faster calculation of the distance from the computation point to the tesseroid and 
(2) the application of a stack based algorithm that speeds up the computation and gives more control over the recursion step.

This forward gravity model has been originally implemented in command line programs written in C programming language. Although, it has been ultimately ported to Python and included in the open-source library Fatiando a Terra \citep{Uieda2013} for geophysical modelling and inversion.

@@

It also makes use of some previously existing classes and functions from Fatiando a Terra, what saved us time and allowed us to focus on the new enhancements. Furthermore, we have the intention to include this new method into a future release of the Fatiando a Terra library in order to make its distribution and maintenance easier.

>>>>

\citet{Uieda2016} developed a forward gravity model based on tesseroids with homogeneous densities using the GLQ approximation method.
It has been originally implemented in command line programs written in C programming language. Although, it has been ultimately ported to Python and included in the open-source library Fatiando a Terra \citep{Uieda2013} for geophysical modelling and inversion.

It's well known that the GLQ method becomes less accurate when the computation point is closer to the tesseroid \citep{Ku1977} or for smaller GLQ degree. 
Although the model developed by \citet{Uieda2016} uses a second GLQ degree, it ensures the accuracy implementing a modified version of the adaptative discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain distance-size ratio ($D$) is greater than a predefined value that controls the precision of the computation.  \citet{Uieda2016} have also objectively obtained standard values of $D$ for gravity potential, gradients and tensor components comparing the fields generated by a spherical shell, which constitutes a special case of the volume integrals that has analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013}\todo{citar mas??}.
The modifications made by \citet{Uieda2016} to the original adaptative discretization method \citep{Li2011} consist in:
(1) a faster calculation of the distance from the computation point to the tesseroid and 
(2) the application of a stack based algorithm that speeds up the computation and gives more control over the recursion step.

@@

It also makes use of some previously existing classes and functions from Fatiando a Terra, what saved us time and allowed us to focus on the new enhancements. Furthermore, we have the intention to include it into a future release of the Fatiando a Terra library in order to make its distribution and maintenance easier.
